On the probability of finding a nonphysical solution through shadowing

### 2020-10-22 main.tex
Adjust fig size

\section{Discussions}
Through a rigorous counter-example, we show that shadowing can lead
to nonphysical solutions.  The conclusion has an immediate implication for
sensitivity analysis methods based on the concept of shadowing \cite{qiqi-lss}\cite{angxiu-lss}\cite{lasagne}.
When the goal is to compute derivatives of ensemble averages, where the ensemble
is distributed according to the physical measure, i.e., the SRB measure, shadowing-based methods can give wrong results.  This has been observed
before and appropriately attributed as ``ergodicity breaking error'' \cite{patrick} \cite{angxiu-error}. In this paper, we construct rigorous analytical examples of this error.

Even more troubling is the implication for numerical simulations of chaotic
governing equations.  Through the examples in this paper, it is clear that a numerical solution, satisfying
a governing equation perturbed due to numerics, is not expected to shadow a
physical solution of the real governing physics.  What is, if any, the
relation of a numerical solution, such as DNS of turbulent flows, to
the true physics? While this question remains open, we conclude with a final example illustrating that not only can shadowing solutions display statistical averages different from physical solutions, but that the difference can be drastic. 
For $10^{-18}$ perturbation (trunction numerically), we get completely different statistics. How can we trust numerical solutions

@@

\begin{figure}
    \centering
    \includegraphics[width=0.35\textwidth,height=2in]{figure/osc_tent_n.png}
    \includegraphics[width=0.35\textwidth,height=2in]{figure/osc_tent_s.png}
    \caption{The plucked tent map shown at different values of $s$ and $n$, that represent the magnitude and frequency of the applied oscillation to the original tent map ($n=0,s=0$). On the left, $s$ is held constant at 0.5. On the right, $n$ is held constant at 0.}
    \label{fig:map}
\end{figure}
[Nisha: shadowing perturabtions predict tiny effects. Real effect is a lot more dramatic. Desmos plot.]
give example of numerics that destroys physicalness

>>>>

\section{Discussions}
Through a rigorous counter-example, we show that shadowing can lead
to nonphysical solutions.  The conclusion has an immediate implication for
sensitivity analysis methods based on the concept of shadowing \cite{qiqi-lss}\cite{angxiu-lss}\cite{lasagne}.
When the goal is to compute derivatives of ensemble averages, where the ensemble
is distributed according to the physical measure, i.e., the SRB measure, shadowing-based methods can give wrong results.  This has been observed
before and appropriately attributed as ``ergodicity breaking error'' \cite{patrick} \cite{angxiu-error}. In this paper, we construct rigorous analytical examples of this error.
\begin{figure}
    \centering
    \includegraphics[width=0.45\textwidth]{figure/osc_tent_n.png}
    \includegraphics[width=0.45\textwidth]{figure/osc_tent_s.png}
    \caption{The plucked tent map shown at different values of $s$ and $n$, that represent the magnitude and frequency of the applied oscillation to the original tent map ($n=0,s=0$). On the left, $s$ is held constant at 0.5. On the right, $n$ is held constant at 0.}
    \label{fig:map}
\end{figure}
Even more troubling is the implication for numerical simulations of chaotic
governing equations.  Through the examples in this paper, it is clear that a numerical solution, satisfying
a governing equation perturbed due to numerics, is not expected to shadow a
physical solution of the real governing physics.  What is, if any, the
relation of a numerical solution, such as DNS of turbulent flows, to
the true physics? While this question remains open, we conclude with a final example illustrating that not only can shadowing solutions display statistical averages different from physical solutions, but that the difference can be drastic. 
For $10^{-18}$ perturbation (trunction numerically), we get completely different statistics. How can we trust numerical solutions

@@

[Nisha: shadowing perturabtions predict tiny effects. Real effect is a lot more dramatic. Desmos plot.]
give example of numerics that destroys physicalness
